OSF management

### 2021-01-31 osf/data/README.Rmd
:bento: - upload TextGrids and READMEs to osf

- The `norming/` directory holds the files of the norming study.
- The `production/` directory contains the `.wav` and `.TextGrid` files from the production experiment.

@@

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

>>>>

- The `norming/` directory holds the files of the norming study.
- The `production/` directory contains two subdirectories:
  - `audio/`: with `.wav` and `.TextGrid` files from the production experiment.
  - `trial-lists/`: with `.csv` files with info on the trials from the production experiment.

@@

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Data component
data_comp <- osf_comps %>% filter(name == "Data")
```

### 2021-01-31 osf/data/norming/ratings/README.Rmd
:bento: - upload TextGrids and READMEs to osf

---
title: "Norming study"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the files of the norming study, designed to obtain typicality ratings of re-colored images of everyday objects.

There are 2 subdirectories:

- The `images/` directory contains the re-colored images used in the norming study.
- The `results/` directory holds an aggregated `tipicality.csv` file with the typicality ratings of each image/object for each participant.

@@

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "norming") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

---
title: "Typicality ratings of the norming study"
output:
  github_document:
    html_preview: false
---

@@

Here you can find an aggregated dataset with the typicality judgement for each of the images in `norming/images/`, for each participant.

@@

### 2021-01-31 osf/manage-osf.Rmd
:bento: - upload TextGrids and READMEs to osf

# Knit readme files

@@

```{r knit-all, message=FALSE, warning=FALSE}
files <- list.files("./osf/comps/data", pattern = "[.]Rmd$", recursive = T, full.names = T)

@@

# Upload files to the OFS repo

```{r readmes}
# A loop would be better
osf_upload(data_comp, path = "./osf/comps/data/README.md", conflicts = "overwrite", verbose = T)

@@

# data/norming/
raw <- data_comp_files %>% filter(name == "norming")

@@

#### upload new readme
osf_upload(
  raw,
  path = "./osf/comps/data/norming/README.md",
  conflicts = "overwrite", verbose = T)

# data/production/audio/
#### delete old readme
old_readme <- osf_ls_files(data_comp, "production/audio", pattern = "README.md")
osf_rm(old_readme, check = FALSE)

#### upload new readme
audio <- osf_ls_files(data_comp, "production", pattern = "audio")
osf_upload(
  audio,
  path = "./osf/comps/data/production/audio/README.md",
  conflicts = "overwrite", verbose = T)

# data/production/trial-lists
#### delete old readme
old_readme <- osf_ls_files(data_comp, "production/trial-lists", pattern = "README.md")
osf_rm(old_readme, check = FALSE)

#### upload new readme
trials <- osf_ls_files(data_comp, "production", pattern = "trial-lists")
osf_upload(
  trials,
  path = "./osf/comps/data/production/trial-lists/README.md",
  conflicts = "overwrite", verbose = T)
```

>>>>

# Readme files

## Knit Readmes

@@

```{r knit-all, message=FALSE, warning=FALSE}
files <- list.files("./osf/data", pattern = "[.]Rmd$", recursive = T, full.names = T)

@@

## Upload Readmes to the OFS repo

```{r readmes}
# A loop would be better

# data/ ----
osf_upload(data_comp, path = "./osf/data/README.md", conflicts = "overwrite", verbose = T)

@@

# data/norming/ ----
raw <- data_comp_files %>% filter(name == "norming")

@@

#### upload new readme
osf_upload(
  raw,
  path = "./osf/data/norming/README.md",
  conflicts = "overwrite", verbose = T)

# data/norming/images/ ----
#### delete old readme
old_readme <- osf_ls_files(data_comp, "norming/images/", pattern = "README.md")
osf_rm(old_readme, check = FALSE)

#### upload new readme
audio <- osf_ls_files(data_comp, "norming", pattern = "images")
osf_upload(
  audio,
  path = "./osf/data/norming/images/README.md",
  conflicts = "overwrite", verbose = T)

# data/production/audio/ ----
#### delete old readme
# old_readme <- osf_ls_files(data_comp, "production/audio", pattern = "README.md")
# osf_rm(old_readme, check = FALSE)
# 
# #### upload new readme
# audio <- osf_ls_files(data_comp, "production", pattern = "audio")
# osf_upload(
#   audio,
#   path = "./osf/data/production/audio/README.md",
#   conflicts = "overwrite", verbose = T)

# data/production/trial-lists ----
#### delete old readme
# old_readme <- osf_ls_files(data_comp, "production/trial-lists", pattern = "README.md")
# osf_rm(old_readme, check = FALSE)
# 
# #### upload new readme
# trials <- osf_ls_files(data_comp, "production", pattern = "trial-lists")
# osf_upload(
#   trials,
#   path = "./osf/data/production/trial-lists/README.md",
#   conflicts = "overwrite", verbose = T)
```

# TextGrids

```{r textgrids, eval=FALSE}
audio <- osf_ls_files(data_comp, "production", pattern = "audio")

# delete old tgs
old_tgs <- osf_ls_files(audio, pattern = ".TextGrid", n_max = Inf)

for (file in 2:nrow(old_tgs)) {
  osf_rm(old_tgs[file,], check = FALSE)
}

# upload new tgs
new_tgs <- list.files("./osf/data/production/audio/", ".TextGrid", full.names = TRUE)

for (tg in new_tgs) {
  osf_upload(
    audio,
    path = tg,
    conflicts = "overwrite", verbose = T
  )
}
```
